\chapter{Conclusion}
Problematic of internship is images noise and denoise. Because all of image noise will be the main cause of image degradation. Denoise solution is very popular to remove noise. In this report we propose main method : median filter, average filter, gaussian filter and wiener filter. MSE and PSNR are 2 quality evaluation method for image when image was remove noise. With values of comparison table, we obtain Wiener filter is the best method. In the future, we will research and improve new methods to solve noise problems in better images.



\begin{thebibliography}{9}
%	\bibitem{Author}
 %   Prof.David Helbert
	
%	\textit{Image Processing
%	To Begin}
	
%	\bibitem{Author}
%Associate professor Chaker Larabi - University of Poitiers
	
%	\textit{Image and Video Processing}

    	\bibitem{Author}
    Mentor-Mr. MANJEET KUMAR

    	
    	\textit{Image De-noising by
    	Various Filters for
    	Different Noise using
    	MATLAB }

\bibitem{Author}
Assistant Professor Monika Kohli, G.C.G Ludhiana

Assistant Professor Harmeet Kaur, G.C.G Ludhiana

\textit{Noise Removal in Image Processing using Median, Adaptive Median and Proposed Median Filter and Respective Image Quality Comparison}

	\bibitem{Author}
	Thierry Blu, Senior Member, IEEE, and Florian Luisier
	
	\textit{The SURE-LET Approach to Image Denoising}





\bibitem{Author}
Chi Chang-yan, Zhang Ji-xian, Liu Zheng-jun

\textit{STUDY ON METHODS OF NOISE REDUCTION IN A STRIPPED IMAGE}

\bibitem{Author}
Gursharan Kaur, Rakesh Kumar, Kamaljeet Kainth

\textit{Different Noise Types and Digital Image Processing}

\bibitem{Author}
Himani Goel, Seema Rani

\textit{A comparative study of Impulse Noise Reduction methods in Digital images}

\bibitem{Author}
 Sunil Kopparapu, M Satish.

\textit{Optimal Gaussian Filter for Effective Noise Filtering}

\bibitem{Author}
 S. Shyam Prasad, R. Priya 
 
 \textit{Image Enhancement with Noise Reduction in Spatial Domain}

\bibitem{Author}
 
 \textit{DIGITAL CAMERA IMAGE NOISE - PART 1}

\texttt{http://www.cambridgeincolour.com/tutorials/image-noise.htm}

\bibitem{Author}
 
 \textit{The Wiener filter}

\texttt{http://homepages.inf.ed.ac.uk/rbf/CVonline/LOCAL\_COPIES/VELDHUIZEN/node15.html}







\end{thebibliography}


































